---
title: 'Homework2: Accelarated Proximal Algrithm for Matrix Completion'
author: "Ya Zhou"
date: "2017/11/1"
output: html_document
---
# The Origima Matrix Taken from Google
- The original matrix img
- Construct the graphics for img
```{r}
library(jpeg)
img = readJPEG("./灰度图.jpg")
img = img[,,1]
par(mar = c(0,0,0,0))
plot(0,0,type = "n")
rasterImage(img, -1, -1, 1, 1)
```

#Cencer Completely at Random 40% information of the Matrix
```{r}
#in order to achieve repetition
set.seed(100)
a<-matrix(,642,500)
for(i in 1:642){
  a[i,]=rep(i,500)
}
b<-matrix(,642,500)
for(i in 1:500){
  b[,i]=rep(i,642)
}
a1<-sample(a,642*500*0.6)
b1<-sample(b,642*500*0.6)
# c1 is the set of coordinates for uncensored point in the matrix
c1<-matrix(c(a1,b1),642*500*0.6,2)
Xomega<-matrix(0,642,500)
X=img
for(i in 1:192600){
  Xomega[c1[i,1],c1[i,2]]=X[c1[i,1],c1[i,2]]
}
#now, the Xomega store the censored data from img
par(mar = c(0,0,0,0))
plot(0,0,type = "n")
rasterImage(Xomega, -1, -1, 1, 1)
```

# the Accerlerated Aproximal Algorithm for Matrix Completion
- We set the tuning parameter of the penalty term lambda=0.1
- The total iteration number is 91

```{r}
library(imageSoft)
img2<-homework2(Xomega,c1,0.1)
par(mar = c(0,0,0,0))
plot(0,0,type = "n")
rasterImage(img2, -1, -1, 1, 1)
```

# Explanation 

# Two papers
- We achieve this based on (2.10) the following paper
- JIAN-FENG CAI⇤, EMMANUEL J. CANDE`S†, AND ZUOWEI SHEN‡.A SINGULAR VALUE THRESHOLDING ALGORITHM FOR MATRIX COMPLETION
- We accelerate (2.10) by referring the folloing paper
- Beck, A., Teboulle, M. (2009) A Fast Iterative Shrinkage-Thresholding Algorithm for Linear Inverse Problems. SIAM J. IMAGING SCIENCES.

# Description for the Algorithm
###The algorithm is based on:
- $X^k =\mathcal{D}_{\lambda \delta_{k-1}}(X^{k-1}+\delta_{k-1}P_{\Omega}(X-X^{k-1}))$ 
- where $\mathcal{D}_{\lambda \delta_{k-1}}$ is the  proximity operator defined in the first paper and $X$ is the input matirx and $\{\delta_k\}$ is a sequence of positive step sizes.

###We rewright it as:
- $X^k=\mathcal{D}_{\lambda \delta_{k-1}}(Y^{k-1})$
- $Y^k=X^k-\delta_{k-1}P_{\Omega}(X-X^{k-1})$
- In my algorithm, I set all the step size $\delta_k=1$

###The above is accelerated by the equation: 
- $Z^k=X^k+(\frac{t_{k-1}-1}{t_k})(X^k-X^{k-1})$
- Replace $X_k$ by $Z^k$, we obtain:
- $Y^k=Z^k-\delta_{k-1}P_{\Omega}(X-Z^{k-1})$
- And $X^{k+1}$ can be updated by
- $X^{k+1}=\mathcal{D}_{\lambda \delta_{k}}(Y^{k})$
- In my algorithm, I set the starting point $t_1=1$ and the updated step of $t_k$ is the same as the content in our class.

#Thanks
###Directed by Shiyuan He
###Written by Ya Zhou
